Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-11 draft.tex
various edits

%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the voting rule is fixed beforehand, and the full preference information is provided by the voters.

%As social choice moves to the web, the
%the need for relaxing the assumptions of classical social choice

In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret.

We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to

We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.

\end{abstract}

@@

In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost).

@@

This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.

We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.

%We argue that it is possible that the committee wants to precise some preferences about the aggregation.s
% Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
%In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
%In this paper we relax the traditional assumptions.

@@

% We must engage in simultaneous elictation of the rule and of the preferences.

@@

%The voting scheme selects the winner (a consensus option).
%Incremental elicitation 
\medskip
The paper is organized as follows.
In Section \ref{sec:background} we provide the necessary background.
We introduce the minimax criterion and in Section \ref{sec:mmr}.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret; finally in Section 
\ref{sec:conclusions} we provide some final thoughts.

@@

We introduce the basic concepts.
We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
The goal of the voters is to make a consensus choice, that is to select a ``winner'' given voter rankings.

>>>>

%Given a full profile: use linear programming to maximize regret
%Given a partial profile: use techniques of Lu and Boutilier (2011).
\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the voting rule is fixed beforehand and full preference information is provided by the voters. 
Recently, the assumption of full preference information has been questioned by a number of researchers and 
number of frameworks for vote elicitation have been proposed.

In this paper we go one step further and we assume that both the voting rule and the voters preferences are partially specified.
Focusing on positional scoring rules, we assume that the chair %is not able to give the definition of the rule but 
is able to answer simple questions  requiring to pick a winner from a specific  example profile.
Moreover, the preferences of the voters are incrementally acquired by asking comparison queries.

We propose a method  for robust approximate winner determination in this setting with minimax regret. 
We then provide an interactive elicitation protocol based on minimax regret
%We then show how minimax regret can be used to drive the elicitation in order to ask informative queries in order to a
and develop several query strategies that interleave questions to the chair and questions to the voters in order to acquire the most relevant information about the preferences and voting rule.
\end{abstract}

@@

%Recently, the assumption of full a has been questioned by a number of researchers
In many real situations, however, it may be necessary to reason with partial preferences, as some preferences are not available and too expensive to obtain (with respect to a cognitive or economic cost). 
This observation has motivated a number of recent works on preference elicitation, including several works on social choice with partial profiles.

We argue that it is possible that the committee wants to precise some preferences about the aggregation.s

@@

We develop methods for computing the minimax-optimal alternative for scoring rules with partial preference information and partial information about the weights.

%
% Incremental elicitation of preferences is critical to easing the cognitive and communication cost for users 
%In this paper we provide a method for approximate winner determination and an incremental elicitation protocol based on minimax regret. 
%In this paper we relax the traditional assumptions.

@@

We develop several query strategies that  focus simultaneously on reduction of relevant preference and voting rule uncertainty.
% We must engage in simultaneous elictation of the rule and of the preferences.

@@

%The voting scheme selects the winner (a consensus option).
%Incremental elicitation 
The paper is organized as follows.
In Section \ref{sec:background} we provide the necessary background.
We introduce the minimax criterion and in Section \ref{sec:mmr}.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret; finally in Section 
\ref{sec:conclusions} we provide some final thoughts.

@@

We introduce the basic concepts.
We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
The goal of the voters is to make a consensus choice, to select a ``winner'' given voter rankings.
